A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-12-20 mod1/response.md

2:
- The SMG is thought to harbor a luminous AGN. In that case, the LIR will certainly have a contribution from the AGN that should be accounted for otherwise the SFR will be overestimated: see e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013, Kirkpatrick+2014. Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting. 
> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). Since we do not have MIR measurements solely from the background SMG and due to the postive K corretion blueward of dust peak, the forground radio galaxy contributes a non-negligible amount to the MIR luminosity, we therefore didn't fit an AGN component. Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand. Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12). We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which is mostly due to SF-driven dust emission.

3:
- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4). These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
> We removed standard equations from the manuscript, and combined the sections reporting SFE, SFR, and SFRSD into one. We also shortened the section.

@@

4:
- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
> We rephrased the introduction to show more clearly the evidence of an AGN.

5:
- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
> We added notes in the caption below Table 4 to recap assumptions used in deriving these quantities.

6:
- Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons? there are many other sources that could be chosen with a range of properties. A comparison to these 2 SMGs is not useful at all given the diversity in this population (e.g. the sentence "This demonstrates the large ..." is not true when comparing only 3 objects). I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.

> We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus would not have been studied in sensitivity-limited samples. In addition, these are among the SMGs which are best-studied to date and their properties are deriving using similar approach in this paper. Hence, a comparison with these object will have relatively lower uncertainties. We have added a compilation of SMG and type-2 QSOs properties to the Table. Please see tablenote and comments for details. We have incoporated a comparison to these values in our conclusion. Please see conclusion section for other changes.

## 7
- the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14. E.g. the last sentence about this SMG transitioning from starburst to QSO phase. How is that conclusion made or strengthened with this new data?

> We updated the conclusions.

# Minor comments
1:
- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs, please see also Table 4.

2:
- section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
> We removed "New results" in the subject headings.

@@

11:
- last few paras of paper: what does "breaking up its dust cocoon" mean? this is the first time this is mentioned and should be explained if it is relevant.
> We mentioned this as a reference from Haas+14. We have removed this phrase in the revised version given that this has been mentioned in Haas+14, and is not necessary in our discussion.

12:
- end of section 4.3.1: the factor of 2 for dust mass is overshadowed by the factor of >5 in alpha_co
> We removed that sentence.

13:
- related to depletion time, there is a new Nature paper by Narayanan et al (published Sept 23) which discusses how SMGs in sims can last for a Gyr with replenishment from the IGM. In that case, is the depletion timescale really useful? what do we learn if the galaxy is getting new gas?
>The derived depletion timescale is derived the based on the definition of the quantity τ = Mgas/SFR, which descibes the time 
it would take for a galaxy to use up the available molecular gas reservoir given the current star formation rate, assuming no 
replenishment of gas (Carilli & Walter 2013). Hence, this quantity provides a lower limit on the timescale for SF activity. 
Based on our observations, we find no evidence of gas inflow in SMMJ0939.

13:
dynamical mass calculation: can you estimate how much higher this would be given observations showing the different radii between the molecular and dust emission in SMGs. How different are the radii?
>The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs. Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on high-J CO measurements. Given the small number statistics on resolved CO(1-0) emission in QSOs, where Riechers+11 find no evidence of extent cold gas emission, we did not include an additional estimate of the dynamical mass assuming some physical size from recent observaitons (still limited) in the paper. However, we have noted these phyiscal sizes in the text, which allows readers to scale the dynamical mass correspondingly should they wish to do so. Please see the revised manuscipt.

### 2015-12-20 mod1/manuscript/ms.tex
put radius instead of physical extent for dust emission size to avoid ambiguity. Updated responses, which is consistent and up to date with changes made to ms.tex
add timestamp to revised version in heading

\slugcomment{Submitted to the ApJ}
\usepackage{amsmath}
\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

@@

\subsubsection{Dynamical Mass}
Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized. With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO. 
We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.  We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii. %\citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}. 
{\bf This has been supported by recent observations. In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}). 
For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
 }

>>>>

\slugcomment{Submitted to the ApJ, Revised version December 20, 2015}
\usepackage{amsmath}
\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

@@

\subsubsection{Dynamical Mass}
Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized. With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO. 
We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.  We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii. %\citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}. 
{\bf This has been supported by recent observations. In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}). 
For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent with radius of 1.2 kpc in a sample of 52 SMGs.
% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
 }
